---
title: "Old Code"
author: "Leo Carlsson"
date: "2/27/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Elections
## Plot Data
```{r Election data, echo=TRUE, message=FALSE, warning=FALSE}
# Data ----------------------------------------------------------------------------------------
# Common
pop <- read_excel("scrape_sweden/pop_sweden_1950-2019.xlsx", 
                  skip = 5) %>% slice(1:290) %>% select(municipality = Kommun,`2002`,`2006`,`2010`,`2014`,`2018`) 
ID <- read_excel("scrape_sweden/kommunlankod27.xls", 
                 skip = 5) %>% select(municipality = Name,
                                      ID = Code,
                                      province = ...3,
                                      province_ID = ...5) %>%
  filter(!str_detect(municipality," län")) %>%
  mutate(muni_ID = ID)


# 2006 ----------------------------------------------------------------------------------------
# Import
elections_sweden <- read_html("https://data.val.se/val/val2006/slutlig/K/rike/delar.html") %>%
  html_table(header = TRUE, fill = TRUE)
elections_sweden <- elections_sweden[[1]]
elections_sweden <- elections_sweden %>% 
  gather(party,vote_share,2:9) %>% 
  arrange(Område) %>% 
  select(municipality = Område,
         party,
         vote_share,
         turnout = VDT) %>%
  filter(!party == "ÖVR") %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))


#Clean away dashes and commas, make data into numeric values 
for(j in 3:ncol(elections_sweden)){
  elections_sweden[,j]=sub("%", "", elections_sweden[,j], fixed = TRUE)
  elections_sweden[,j]=as.numeric(sub(",", ".", elections_sweden[,j], fixed = TRUE))
}

other <- read_excel("scrape_sweden/election_2006.xls", 
                    sheet = "Tabell 9", skip = 6) %>% slice(6:373) %>%
  select(municipality = Kommun,
         party = ...2,
         votes = Antal,
         vote_share = `% av samtliga giltiga röster`,
         seats_won = Totalt) %>%
  filter(!is.na(vote_share)) %>%
  mutate(municipality = if_else(municipality == "Heby2", "Heby", municipality)) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality)) %>%
  mutate(party = if_else(party == "Sverigedemokraterna", "SD", party)) %>%
  mutate(party = if_else(party == "SPI - Sveriges Pensionärers Intresseparti", "SPI", party)) %>% 
  fill(municipality)


elections_sweden <- merge(elections_sweden, pop, by = "municipality", all = TRUE)
elections_sweden <- elections_sweden %>% select(-`2010`,-`2014`,-`2018`,-`2002`) %>%
  rename(pop = `2006`)
elections_sweden <- merge(elections_sweden, ID, by = "municipality", all = TRUE)

#Seats        
mandates <- read_html("https://data.val.se/val/val2006/slutlig_ovrigt/statistik/kommun/mandat_kommun_parti.html") %>%
  html_table(header = TRUE, fill = TRUE) %>%
  first() %>% filter(Kommun != "SUMMA") %>%
  gather(party,seats_won,2:11) %>% 
  rename(municipality = Kommun,
         mandates = TOT) %>% 
  separate_rows(seats_won, sep = ", ") %>% #These could be split into separate rows using gsub and regular expressions
  na_if("") %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality)) %>%
  group_by(municipality) %>%
  mutate(nParties = sum(!is.na(seats_won))) %>%
  filter(!is.na(seats_won)) %>%
  arrange(municipality)

local <- merge(elections_sweden,mandates, by = c("municipality", "party"), all = TRUE)

local <- local %>% mutate(cname = "Sweden",
                          ccode = "SE",
                          date = "2006-09-17",
                          clevel = "municipality")

voter <- read_excel("scrape_sweden/election_2006.xls", 
                    sheet = "Tabell 7", skip = 5) %>% 
  select(municipality = ...1,
         eligible_voters = ...3,
         total_voters = ...5,
         valid_votes = ...10,
         M=m,C=c,FP=fp,KD=kd,MP=mp,S=s,V=v,ÖVR=övr)%>%
  mutate(municipality = if_else(municipality == "Heby2", "Heby", municipality)) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality)) %>%
  filter(!str_detect(municipality," län")) %>% #NOTE space before län! if not, removes the muni Borlänge
  filter(!is.na(municipality)) %>% 
  filter(municipality != "Hela riket") %>%
  slice(-291:-293) %>%
  gather(party,votes,5:12) %>%
  arrange(municipality)

local <- merge(local,voter, by = c("municipality", "party"), all = TRUE) %>% 
  filter(!party == "SD") %>%
  filter(!party == "ÖVR")
local <- merge(local, other, by = c("municipality","votes","party","vote_share","seats_won"), all = TRUE) %>% 
  arrange(municipality, turnout)
local <- local %>% mutate(seats_won = ifelse(is.na(seats_won), 0, seats_won)) %>% 
  fill(turnout:valid_votes) %>% 
  select(cname, ccode, date, clevel, turnout, ID,
         province_ID, province, muni_ID, municipality, pop, eligible_voters, total_voters,
         valid_votes, party, votes, vote_share, seats_won, mandates, nParties) %>%
  arrange(date, municipality, desc(vote_share))

sweden_plot <- local



# 2010 ----------------------------------------------------------------------------------------
# Import
elections_sweden <- read_html("https://data.val.se/val/val2010/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
elections_sweden <- elections_sweden[[2]]

elections_sweden <- elections_sweden[,c(1,2,4,6,8,10,12,14,16,18,20,22,24)] %>%
  gather(party,vote_share, 2:9) %>%
  arrange(Område) %>% 
  select(municipality = Område,
         party,
         vote_share,
         turnout = VDT) %>% 
  filter(!municipality == "Sverige")


votes <- read_html("https://data.val.se/val/val2010/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
votes <- votes[[2]]
votes <- votes[,c(1,3,5,7,9,11,13,15,17)] %>%
  gather(party,votes, 2:9) %>%
  rename(municipality = Område)%>% 
  filter(!municipality == "Sverige")
elections_sweden <- merge(elections_sweden, votes, by = c("municipality", "party"))

#Clean away dashes and commas, make data into numeric values 
for(j in 3:ncol(elections_sweden)){
  elections_sweden[,j]=sub("%", "", elections_sweden[,j], fixed = TRUE)
  elections_sweden[,j]=as.numeric(sub(",", ".", elections_sweden[,j], fixed = TRUE))
}

#Getting the non-national parties
other <- read_excel("scrape_sweden/election_2010.xls", 
                    sheet = "Tabell 11", skip = 11) %>%
  select(municipality = `Stockholms län`,
         party = ...3,
         votes = ...4,
         vote_share = ...5,
         seats_won = ...9)%>%
  filter(!is.na(vote_share)) %>%
  fill(municipality) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))

elections_sweden <- merge(elections_sweden, other, by = c("municipality","party","votes","vote_share"), all = TRUE)
elections_sweden <- elections_sweden %>% arrange(municipality, turnout) %>%
  fill(turnout)

#Seats for national parties        
mandates <- read_html("https://data.val.se/val/val2010/slutresultat/K/rike/valda.html") %>%
  html_table(header = TRUE, fill = TRUE)
mandates <- mandates[[2]] %>% filter(Område != "Sverige") %>%
  gather(party,seats_won,2:9) %>% 
  rename(municipality = Område,
         mandates = TOT) %>% 
  group_by(municipality) %>%
  mutate(nParties = sum(!is.na(seats_won))) %>%
  mutate(seats_won = ifelse(is.na(seats_won),0,seats_won)) %>%
  arrange(municipality) %>% select(-ÖVR)

#Merge seats and all other election data
local <- merge(elections_sweden,mandates, by = c("municipality", "party"), all = TRUE)
local <- local %>% mutate(seats_won = if_else(is.na(seats_won.x), seats_won.y, seats_won.x))%>%
  select(-seats_won.x, -seats_won.y) %>% arrange(municipality, mandates) %>%
  fill(mandates:nParties)


#generate the static variables
local <- local %>% mutate(cname = "Sweden",
                          ccode = "SE",
                          date = "2010-09-19",
                          clevel = "municipality")
#pop data and IDs
local <- merge(local, pop, by = "municipality", all = TRUE)
local <- local %>% select(-`2006`,-`2014`,-`2018`,-`2002`) %>%
  rename(pop = `2010`)
local <- merge(local, ID, by = "municipality", all = TRUE)

#Voter data
voter <- read_excel("scrape_sweden/election_2010.xls", 
                    sheet = "Tabell 9", skip = 5) %>% 
  select(municipality = ...1,
         eligible_voters = `berät-`,
         total_voters = ...5,
         valid_votes = giltiga) %>%
  slice(7:336) %>%
  filter(!str_detect(municipality," län")) %>% #NOTE space before län! if not, removes the muni Borlänge
  filter(!is.na(municipality)) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))

local <- merge(local,voter, by = "municipality", all = TRUE)

#reorder and arrange
local <- local %>% select(cname, ccode, date, clevel, turnout, ID,
                          province_ID, province, muni_ID, municipality, pop, eligible_voters, total_voters,
                          valid_votes, party, votes, vote_share, seats_won, mandates, nParties) %>%
  arrange(date, municipality, desc(vote_share))

sweden_plot <- rbind(sweden_plot, local)


# 2014 ----------------------------------------------------------------------------------------
# Import
elections_sweden <- read_html("https://data.val.se/val/val2014/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
elections_sweden <- elections_sweden[[2]]

elections_sweden <- elections_sweden[,c(1,2,4,6,8,10,12,14,16,18,20,22,24,26)] %>%
  gather(party,vote_share, 2:10) %>%
  arrange(Område) %>% 
  select(municipality = Område,
         party,
         vote_share,
         turnout = VDT)%>% 
  filter(!municipality == "Sverige")

votes <- read_html("https://data.val.se/val/val2014/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
votes <- votes[[2]]
votes <- votes[,c(1,3,5,7,9,11,13,15,17,19)] %>%
  gather(party,votes, 2:10) %>% #Fi!
  rename(municipality = Område) %>% 
  filter(!municipality == "Sverige")

elections_sweden <- merge(elections_sweden, votes, by = c("municipality", "party"))
rm(votes)

#Clean away dashes and commas, make data into numeric values 
for(j in 3:ncol(elections_sweden)){
  elections_sweden[,j]=sub("%", "", elections_sweden[,j], fixed = TRUE)
  elections_sweden[,j]=as.numeric(sub(",", ".", elections_sweden[,j], fixed = TRUE))
}
rm(j)

#Getting the non-national parties
other <- read_excel("scrape_sweden/election_2014.xlsx", 
                    sheet = "Tabell 11", skip = 11) %>%
  select(municipality = `Stockholms län`,
         party = ...3,
         votes = ...4,
         vote_share = ...5,
         seats_won = ...9)%>%
  filter(!is.na(vote_share)) %>% 
  filter(!party == "Feministiskt initiativ")%>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))

elections_sweden <- merge(elections_sweden, other, by = c("municipality","party","votes","vote_share"), all = TRUE)
elections_sweden <- elections_sweden %>% arrange(municipality, turnout) %>%
  fill(turnout)
rm(other)

#Seats for national parties        
mandates <- read_html("https://data.val.se/val/val2014/slutresultat/K/rike/valda.html") %>%
  html_table(header = TRUE, fill = TRUE)
mandates <- mandates[[2]] %>% filter(Område != "Sverige") %>%
  gather(party,seats_won,2:10) %>% #Fi!
  rename(municipality = Område,
         mandates = TOT) %>% 
  group_by(municipality) %>%
  mutate(nParties = sum(!is.na(seats_won))) %>%
  mutate(seats_won = ifelse(is.na(seats_won),0,seats_won)) %>%
  arrange(municipality) %>% select(-ÖVR)

#Merge seats and all other election data
local <- merge(elections_sweden,mandates, by = c("municipality", "party"), all = TRUE)
local <- local %>% mutate(seats_won = if_else(is.na(seats_won.x), seats_won.y, seats_won.x))%>%
  select(-seats_won.x, -seats_won.y) %>% arrange(municipality, mandates) %>%
  fill(mandates:nParties)
rm(mandates)

#generate the static variables
local <- local %>% mutate(cname = "Sweden",
                          ccode = "SE",
                          date = "2014-09-14",
                          clevel = "municipality")
#pop data and IDs
local <- merge(local, pop, by = "municipality", all = TRUE)
local <- local %>% select(-`2006`,-`2010`,-`2018`,-`2002`) %>%
  rename(pop = `2014`)
local <- merge(local, ID, by = "municipality", all = TRUE)

#Voter data
voter <- read_excel("scrape_sweden/election_2014.xlsx", 
                    sheet = "Tabell 9", skip = 5) %>% 
  select(municipality = ...1,
         eligible_voters = `berät-`,
         total_voters = ...3,
         valid_votes = giltiga) %>%
  slice(7:336) %>%
  filter(!str_detect(municipality," län")) %>% #NOTE space before län! if not, removes the muni Borlänge
  filter(!is.na(municipality)) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))

local <- merge(local,voter, by = "municipality", all = TRUE)
rm(voter)

#reorder and arrange
local <- local %>% select(cname, ccode, date, clevel, turnout, ID,
                          province_ID, province, muni_ID, municipality, pop, eligible_voters, total_voters,
                          valid_votes, party, votes, vote_share, seats_won, mandates, nParties) %>%
  arrange(date, municipality, desc(vote_share))

sweden_plot <- rbind(sweden_plot, local)


# 2018 ----------------------------------------------------------------------------------------
# Import
elections_sweden <- read_html("https://data.val.se/val/val2018/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
elections_sweden <- elections_sweden[[2]]
elections_sweden <- elections_sweden[,c(1,2,4,6,8,10,12,14,16,18,20,22,24,26,28)] %>%
  gather(party,vote_share, 2:10) %>%
  arrange(Område) %>% 
  select(municipality = Område,
         party,
         vote_share,
         turnout = VDT)%>% 
  filter(!municipality == "Sverige")

votes <- read_html("https://data.val.se/val/val2018/slutresultat/K/rike/index.html") %>%
  html_table(header = TRUE, fill = TRUE)
votes <- votes[[2]]
votes <- votes[,c(1,3,5,7,9,11,13,15,17,19)] %>%
  gather(party,votes, 2:10) %>% #Fi!
  rename(municipality = Område)%>% 
  filter(!municipality == "Sverige")
elections_sweden <- merge(elections_sweden, votes, by = c("municipality", "party"))
rm(votes)

#Clean away dashes and commas, make data into numeric values 
for(j in 3:ncol(elections_sweden)){
  elections_sweden[,j]=sub("%", "", elections_sweden[,j], fixed = TRUE)
  elections_sweden[,j]=as.numeric(sub(",", ".", elections_sweden[,j], fixed = TRUE))
}
rm(j)

#Getting the non-national parties
other <- read_excel("scrape_sweden/other_2018.xlsx", skip = 11) %>%
  select(municipality = `Stockholms län`,
         party = ...3,
         votes = ...4,
         vote_share = ...5,
         seats_won = ...9)%>%
  filter(!is.na(vote_share))%>%
  filter(!party == "Feministiskt initiativ") %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality))

elections_sweden <- merge(elections_sweden, other, by = c("municipality","party","votes","vote_share"), all = TRUE)
elections_sweden <- elections_sweden %>% arrange(municipality, turnout) %>%
  fill(turnout)
rm(other)

#Seats for national parties        
mandates <- read_html("https://data.val.se/val/val2018/slutresultat/K/rike/valda.html") %>%
  html_table(header = TRUE, fill = TRUE)
mandates <- mandates[[2]] %>% filter(Område != "Sverige") %>%
  gather(party,seats_won,2:10) %>% #Fi!
  rename(municipality = Område,
         mandates = TOT) %>% 
  group_by(municipality) %>%
  mutate(seats_won = ifelse(is.na(seats_won),0,seats_won)) %>%
  arrange(municipality) %>% select(-ÖVR)

#Merge seats and all other election data
local <- merge(elections_sweden,mandates, by = c("municipality", "party"), all = TRUE)
local <- local %>% mutate(seats_won = if_else(is.na(seats_won.x), seats_won.y, seats_won.x))%>%
  select(-seats_won.x, -seats_won.y) %>% arrange(municipality, mandates) %>% 
  fill(mandates)
rm(mandates)

#generate the static variables
local <- local %>% mutate(cname = "Sweden",
                          ccode = "SE",
                          date = "2018-09-09",
                          clevel = "municipality")
#pop data and IDs
local <- merge(local, pop, by = "municipality", all = TRUE)
local <- local %>% select(-`2006`,-`2010`,-`2014`,-`2002`) %>%
  rename(pop = `2018`)
local <- merge(local, ID, by = "municipality", all = TRUE)

#Voter data
voter <- read_excel("scrape_sweden/election_2018.xlsx", 
                    skip = 5) %>% 
  select(municipality = ...1,
         eligible_voters = tigade,
         total_voters = ...3,
         valid_votes = `val-`) %>%
  slice(6:388) %>%
  mutate(municipality = if_else(municipality == "Malung", "Malung-Sälen",municipality)) %>%
  filter(municipality %in% ID$municipality)

local <- merge(local,voter, by = "municipality", all = TRUE)
rm(voter)

local <- local %>% group_by(municipality) %>% 
  mutate(seatsCount = ifelse(seats_won == 0, NA, seats_won)) %>%
  mutate(nParties = sum(!is.na(seatsCount))) %>% ungroup()

#reorder and arrange
local <- local %>% select(cname, ccode, date, clevel, turnout, ID,
                          province_ID, province, muni_ID, municipality, pop, eligible_voters, total_voters,
                          valid_votes, party, votes, vote_share, seats_won, mandates, nParties) %>%
  arrange(date, municipality, desc(vote_share))

sweden_plot <- rbind(sweden_plot, local)
rm(local)
rm(elections_sweden)

sweden_plot <- sweden_plot %>%  mutate(party = if_else(party == "FP", "L", party)) %>% select(-cname,-ccode,-clevel)


# 2002 ----------------------------------------------------------------------------------------
#missing local parties
# 2002
elections_sweden <- read_excel("scrape_sweden/2002_votes.xlsx", skip = 3) %>% 
  select(muni_ID = ...1,
         municipality = ...2,
         party = ...3,
         votes = `2002...5`,
         vote_share = `2002...6`) %>%
  fill(muni_ID,municipality) %>%
  slice(1:3201) %>%
  filter(municipality != "Bara")

votes <- elections_sweden %>% group_by(municipality) %>%
  mutate(eligible_voters = sum(votes)) %>%
  filter(party != "VALSKOLKARE") %>% 
  mutate(total_voters = sum(votes)) %>%
  filter(party != "OGILTIGA") %>%
  mutate(valid_votes = sum(votes)) %>%
  mutate(turnout = total_voters/eligible_voters) %>%
  filter(party == "M") %>%
  filter(municipality != "Bara") %>%
  select(muni_ID, municipality, eligible_voters:turnout)

elections_sweden <- merge(elections_sweden, votes, by = c("muni_ID", "municipality"))     
rm(votes)

mandates <- read_excel("scrape_sweden/2002_mandates.xlsx", skip = 1) %>% 
  select(muni_ID = ...1,
         municipality = ...2,
         party = ...3,
         seats_won = `2002`) %>%
  fill(muni_ID,municipality) %>%
  slice(1:2619) %>%
  mutate(seats_won = as.integer(seats_won)) %>%
  group_by(municipality) %>%
  mutate(mandates = sum(seats_won)) %>%
  filter(!is.na(seats_won))

elections_sweden <- merge(elections_sweden, mandates, by = c("muni_ID", "municipality", "party"))
rm(mandates)

elections_sweden <- merge(elections_sweden, pop, by = "municipality", all = TRUE)
elections_sweden <- elections_sweden %>% select(-`2006`,-`2010`,-`2014`,-`2018`) %>%
  rename(pop = `2002`)
elections_sweden <- merge(elections_sweden, ID, by = c("municipality","muni_ID"), all = TRUE)

elections_sweden <- elections_sweden %>%
  mutate(date = "2002-09-15",
         nParties = NA,
         party = if_else(party == "FP", "L", party)) %>%
  select(date, turnout, ID,
         province_ID, province, muni_ID, municipality, pop, eligible_voters, total_voters,
         valid_votes, party, votes, vote_share, seats_won, mandates, nParties)
sweden_plot <- rbind(sweden_plot, elections_sweden)
rm(elections_sweden)

# misc ----------------------------------------------------------------------------------------
sweden_plot <- sweden_plot %>% mutate(turnout = as.numeric(turnout),
                            eligible_voters = as.integer(eligible_voters),
                            valid_votes = as.integer(valid_votes),
                            votes = as.integer(votes),
                            vote_share = as.numeric(vote_share),
                            seats_won = as.integer(seats_won))
procurement <- read_dta("./Data/procurement/bdf_replication.dta")
```

## Audit and naming of chair in the auditing commitee 
http://www.statistikdatabasen.scb.se/sq/82272, 1 = minority chairman, 0 = majority 
```{r Revision, message=FALSE}
audit <- read_excel("./scrape_sweden/audit.xlsx", skip = 2, na ="..") %>% 
  rename(muni_ID=...1,
         municipality = ...2) %>%
  slice(1:290) %>%
  gather(year, auditor,3:6) %>% 
  mutate(auditor = ifelse(auditor==1, "minority",auditor)) %>% 
  mutate(auditor = ifelse(auditor==0, "majority",auditor)) %>%
  arrange(muni_ID, year)
```






## Scraping majorities 2014
From https://sv.wikipedia.org/wiki/Lista_%C3%B6ver_kommun-_och_landstingsstyren_i_Sverige_2014%E2%80%932018, copied into excel and cleaned by hand. This is due to the irregular table used by wikipedia, which makes web scraping beyond my capabilities. Risk of errors increase
```{r Majorities 2014}
major_2014 <- tribble(
    ~municipality,  ~rule,                   ~num_mandates,
    "Karlshamn",	"S+C+L",	"26 av 51",
    "Karlskrona",	"S+C+L",	"38 av 75",
    "Olofström",	"S",	"25 av 49",
    "Ronneby",	"M+C+L+ROP+KD",	"19 av 49 (minoritet)",
    "Sölvesborg",	"S+V+MP",	"24 av 49 (minoritet)",
    "Avesta",	"S",	"21 av 41",
    "Borlänge",	"S+V+MP+OFA",	"31 av 61",
    "Falun",	"S+C+MP",	"31 av 61",
    "Gagnef",	"S+KOSA+MP+V",	"19 av 35",
    "Hedemora",	"S+C+V",	"23 av 41",
    "Leksand",	"C+M+KD+L",	"24 av 49 (minoritet)",
    "Ludvika",	"S+V+MP",	"24 av 45",
    "Malung-Sälen",	"S+C+V",	"23 av 39",
    "Mora",	"C+M+MOP+KD+L",	"22 av 41",
    "Orsa",	"C+MP+M+KD+L",	"16 av 31",
    "Rättvik",	"C+M+L+KD",	"20 av 39",
    "Smedjebacken",	"S+V+MP",	"20 av 35",
    "Säter",	"S+C",	"20 av 35",
    "Vansbro",	"C+S",	"21 av 31",
    "Älvdalen",	"S+MP",	"18 av 35",
    "Gotland",	"S+MP+V",	"36 av 71",
    "Bollnäs",	"S+V+MP+L",	"21 av 45 (minoritet)",
    "Gävle",	"S+V+MP(2014–2015)",	"30 av 65 (minoritet)",
    "Gävle",	"M+L+C+KD(2015–)",	"27 av 65 (minoritet)",
    "Hofors",	"S+V(2014–2017)",	"16 av 31",
    "Hofors",	"S+L+C(2017–)",	"16 av 31",
    "Hudiksvall",	"S+V",	"25 av 51 (minoritet)",
    "Ljusdal",	"M+V+C+L+KD",	"19 av 41 (minoritet)",
    "Nordanstig",	"S+C+MP",	"17 av 31",
    "Ockelbo",	"S+C",	"20 av 31",
    "Ovanåker",	"S+M+MP+L",	"17 av 41 (minoritet)",
    "Sandviken",	"S+C+MP",	"26 av 51",
    "Söderhamn",	"S+V+MP",	"24 av 49",
    "Falkenberg",	"C+M+MP+L+KD",	"25 av 51 (minoritet)",
    "Halmstad",	"M+C+L+MP+SPI+KD(2014–2016)",	"36 av 71",
    "Halmstad",	"M+C+L+MP+KD(2016–2017)",	"34 av 71 (minoritet)",
    "Halmstad",	"M+C+L+MP+KD+vildar(2017–)",	"36 av 71",
    "Hylte",	"S+L+V+MP+SPI",	"20 av 39",
    "Kungsbacka",	"M+C+L+KD",	"36 av 61",
    "Laholm",	"M+C+MP+KD+L",	"22 av 41 (2014–2016)",
    "Laholm",	"M+C+MP+KD+L",	"20 av 41 (minoritet, 2016–)",
    "Varberg",	"M+C+MP+L+KD",	"31 av 61",
    "Berg",	"S+MP",	"15 av 31 (minoritet)",
    "Bräcke",	"S+LFIB+V+L",	"20 av 39",
    "Härjedalen",	"S+VH+V(2014–2016)",	"19 av 39 (minoritet)",
    "Härjedalen",	"C+M+L(2016–)",	"14 av 39 (minoritet)",
    "Krokom",	"C+M+MP+KD",	"22 av 45 (minoritet)",
    "Ragunda",	"S",	"15 av 27",
    "Strömsund",	"S+V",	"20 av 35",
    "Åre",	"S+M+MP",	"21 av 37",
    "Östersund",	"S+MP+V",	"32 av 61",
    "Aneby",	"C+KD+M+L",	"18 av 35",
    "Eksjö",	"C+M+KD+L",	"26 av 49",
    "Gislaved",	"S+M+MP",	"31 av 49",
    "Gnosjö",	"M+KD+C+L",	"17 av 35 (minoritet)",
    "Habo",	"S+KD+MP+C",	"20 av 35",
    "Jönköping",	"M+KD+C+L(2014–2017)",	"37 av 81 (minoritet)",
    "Jönköping",	"M+KD+C+L(2017–)",	"33 av 81 (minoritet)",
    "Mullsjö",	"S+MP+V",	"15 av 35 (minoritet)",
    "Nässjö",	"S+M+C+V",	"30 av 57",
    "Sävsjö",	"S+KD+C",	"25 av 39",
    "Tranås",	"M+C+KD+L",	"17 av 41 (minoritet)",
    "Vaggeryd",	"M+KD+C+L",	"18 av 41 (minoritet)",
    "Vetlanda",	"S+VF",	"21 av 45 (minoritet)",
    "Värnamo",	"M+C+KD+L",	"23 av 51 (minoritet)",
    "Borgholm",	"S+FÖL",	"16 av 35 (minoritet)",
    "Emmaboda",	"S+V+MP(2014–2015)",	"22 av 41",
    "Emmaboda",	"S+V(2015–)",	"20 av 41 (minoritet)",
    "Hultsfred",	"C+M+KD+L+MP",	"21 av 45 (minoritet)",
    "Högsby",	"C+M+KD",	"14 av 35 (minoritet)",
    "Kalmar",	"S+C+V",	"36 av 61",
    "Mönsterås",	"C+M+KD+L",	"24 av 49 (minoritet)",
    "Mörbylånga",	"M+C+MP+L+KD",	"27 av 49",
    "Nybro",	"C+M+KD+L+SPI(2014-2015)",	"23 av 49 (minoritet)",
    "Nybro",	"C+M+KD+L+SPI(2015–)",	"22 av 49 (minoritet)",
    "Oskarshamn",	"S+V+C+MP",	"26 av 49",
    "Torsås",	"S+M+L+MP+KD+V",	"19 av 35",
    "Vimmerby",	"S+M",	"29 av 49",
    "Västervik",	"S+C+MP",	"29 av 57",
    "Alvesta",	"S+C+MP",	"23 av 49 (minoritet)",
    "Lessebo",	"S+C",	"21 av 35",
    "Ljungby",	"M+C+L+KB",	"20 av 49 (minoritet)",
    "Markaryd",	"KD+C+M",	"20 av 35",
    "Tingsryd",	"S+M",	"21 av 41",
    "Uppvidinge",	"C+KD",	"11 av 41 (minoritet)",
    "Växjö",	"M+C+MP+L+KD",	"33 av 61",
    "Älmhult",	"S+V+MP",	"19 av 41 (minoritet)",
    "Arjeplog",	"S",	"8 av 21 (minoritet)",
    "Arvidsjaur",	"S+V",	"16 av 29",
    "Boden",	"S+NS+MP+L+KD",	"25 av 49",
    "Gällivare",	"V+M+MP+NS+MV",	"22 av 41",
    "Haparanda",	"S+V",	"19 av 35",
    "Jokkmokk",	"S+V",	"16 av 31",
    "Kalix",	"S+MP+V",	"25 av 41",
    "Kiruna",	"S+V+M+SL+FI",	"24 av 45",
    "Luleå",	"S+MP",	"35 av 61",
    "Pajala",	"S+V",	"22 av 33",
    "Piteå",	"S+V+MP",	"30 av 51",
    "Älvsbyn",	"S+V",	"18 av 31",
    "Överkalix",	"V+C+M+MP",	"17 av 31",
    "Övertorneå",	"C+ÖFA+NS+KD+M",	"18 av 31",
    "Bjuv",	"S+C+L+KD",	"18 av 31",
    "Bromölla",	"S+M+A+V+MP",	"29 av 41",
    "Burlöv",	"S+MP+V+C",	"21 av 41",
    "Båstad",	"BJP+C+KD(2014–2015)",	"15 av 41 (minoritet)",
    "Båstad",	"BJP(2015–)",	"13 av 41 (minoritet)",
    "Eslöv",	"S+M",	"26 av 51",
    "Helsingborg",	"M+L+C+KD+MP",	"33 av 65",
    "Hässleholm",	"S+C+MP+V(2014–2017)",	"30 av 61 (minoritet)",
    "Hässleholm",	"M+KD+L(2017–)",	"15 av 61 (minoritet)",
    "Höganäs",	"M+L+C+KD",	"25 av 41",
    "Hörby",	"S+C+L+MP+KD",	"21 av 41",
    "Höör",	"S+MP+V+M+C+KD",	"30 av 41",
    "Klippan",	"S+C+MP+V",	"21 av 41",
    "Kristianstad",	"S+L+C",	"38 av 71",
    "Kävlinge",	"M+L+MP+C+KD",	"27 av 49",
    "Landskrona",	"L+M+MP",	"20 av 51 (minoritet)",
    "Lomma",	"M+L+C+KD",	"29 av 45",
    "Lund",	"S+MP+V+FI(2014–2015)",	"31 av 65 (minoritet)",
    "Lund",	"S+MP+FI(2015)",	"26 av 65 (minoritet)",
    "Lund",	"S+MP(2015–)",	"24 av 65 (minoritet)",
    "Malmö",	"S+MP+V(2014–2015)",	"33 av 61",
    "Malmö",	"S+MP(2015–)",	"27 av 61 (minoritet)",
    "Osby",	"S+V+MP",	"19 av 41 (minoritet)",
    "Perstorp",	"S+M+C+KD",	"18 av 35",
    "Simrishamn",	"S+ÖSTP+C+MP+L",	"26 av 49",
    "Sjöbo",	"M+C+KD+SJP+L",	"25 av 49",
    "Skurup",	"S+KV+MP+V",	"18 av 41 (minoritet)",
    "Staffanstorp",	"M+L+C+KD",	"20 av 41 (minoritet)",
    "Svalöv",	"S+M+L(2014-2018)",	"17 av 35 (minoritet)",
    "Svalöv",	"S+C+MP+V+FI(2018-)",	"20 av 35",
    "Svedala",	"M+L+BAP+C",	"19 av 45 (minoritet)",
    "Tomelilla",	"C+M+MP+L+SPI+KD",	"20 av 41 (minoritet)",
    "Trelleborg",	"S+MP+C+Söderslättspartiet",	"27 av 51",
    "Vellinge",	"M",	"26 av 51",
    "Ystad",	"S+C+V",	"25 av 49",
    "Åstorp",	"S+C+KD",	"17 av 31",
    "Ängelholm",	"S+EP+MP+L",	"26 av 51",
    "Örkelljunga",	"M+KD+C+L",	"17 av 41 (minoritet)",
    "Östra Göinge",	"M+L+C+KD+MP",	"13 av 31 (minoritet)",
    "Botkyrka",	"S+MP+V",	"35 av 61",
    "Danderyd",	"M+L+KD",	"30 av 45",
    "Ekerö",	"M+L+C+KD(2014–2017)",	"24 av 41",
    "Ekerö",	"M+C+KD(2017–)",	"21 av 41",
    "Haninge",	"S+C+MP",	"27 av 61 (minoritet)",
    "Huddinge",	"M+L+C+DP+KD+HP",	"29 av 61 (minoritet)",
    "Järfälla",	"S+MP+C",	"29 av 61 (minoritet)",
    "Lidingö",	"M+LP+KD",	"27 av 51",
    "Nacka",	"M+L+C+KD",	"34 av 61",
    "Norrtälje",	"S+C+MP",	"30 av 61 (minoritet)",
    "Nykvarn",	"NP+M+C(2014–2016)",	"18 av 31",
    "Nykvarn",	"NP+M(2016–)",	"16 av 31",
    "Nynäshamn",	"S+L+MP",	"17 av 41 (minoritet)",
    "Salem",	"M+L+C+KD",	"16 av 31",
    "Sigtuna",	"S+MP+L(2014–2017)",	"25 av 51 (minoritet)",
    "Sigtuna",	"M+L+MP+KD+SFS+C(2017–)",	"25 av 51 (minoritet)",
    "Sollentuna",	"M+L+KD",	"32 av 61",
    "Solna",	"M+L+C+KD",	"30 av 61 (minoritet)",
    "Stockholm",	"S+MP+V+FI",	"53 av 101",
    "Sundbyberg",	"S+V+C+KD(2014–2015)",	"27 av 55 (minoritet)",
    "Sundbyberg",	"M+MP+L+C+KD(2015–)",	"29 av 55",
    "Södertälje",	"S+MP+V",	"33 av 61",
    "Tyresö",	"M+L+C+KD",	"26 av 51",
    "Täby",	"M+L+C+KD",	"46 av 61",
    "Upplands Bro",	"S+MP+KD+C",	"21 av 41",
    "Upplands Väsby",	"S+MP+V+VB",	"27 av 51",
    "Vallentuna",	"M+C+L+KD",	"23 av 41",
    "Vaxholm",	"M+L+C",	"16 av 31",
    "Värmdö",	"M+L+KD+C",	"26 av 51",
    "Österåker",	"M+L+C+KD+ÖP",	"25 av 51 (minoritet)",
    "Eskilstuna",	"S+M+C",	"47 av 79",
    "Flen",	"S+C+KD+MP",	"25 av 45",
    "Gnesta",	"S+M",	"18 av 31",
    "Katrineholm",	"S+M",	"30 av 51",
    "Nyköping",	"S+MP+V",	"31 av 61",
    "Oxelösund",	"S+V",	"17 av 31",
    "Strängnäs",	"M+S",	"31 av 55",
    "Trosa",	"M+C+L+KD",	"22 av 35",
    "Vingåker",	"S+MP+V",	"15 av 31 (minoritet)",
    "Enköping",	"S+NE",	"24 av 51 (minoritet)",
    "Heby",	"C+M+L-P+MP+KD+L",	"20 av 41 (minoritet)",
    "Håbo",	"M+C+MP+L+KD",	"18 av 41 (minoritet)",
    "Knivsta",	"M+C+KD+L",	"15 av 31 (minoritet)",
    "Tierp",	"S+MP",	"23 av 49 (minoritet)",
    "Uppsala",	"S+MP+V",	"42 av 81",
    "Älvkarleby",	"S+MP+V",	"16 av 31",
    "Östhammar",	"S+C",	"28 av 49",
    "Arvika",	"S",	"23 av 49 (minoritet)",
    "Eda",	"HEL+V",	"13 av 35",
    "Filipstad",	"S+V+MP",	"19 av 37",
    "Forshaga",	"S+V+MP",	"23 av 41",
    "Grums",	"S",	"16 av 31",
    "Hagfors",	"S",	"19 av 35",
    "Hammarö",	"S+V+C",	"17 av 31",
    "Karlstad",	"M+MP+L+C+KD",	"31 av 61",
    "Kil",	"S+C",	"20 av 35",
    "Kristinehamn",	"S+V+MP",	"21 av 41",
    "Munkfors",	"S",	"15 av 25",
    "Storfors",	"S+V",	"16 av 27",
    "Sunne",	"S+HS+MP+V",	"20 av 41 (minoritet) 2014–2016",
    "Sunne",	"C+M+L",	"17 av 41 (minoritet) 2016-",
    "Säffle",	"M+SIV+L+C+KD",	"23 av 41",
    "Torsby",	"S+C+L",	"19 av 31",
    "Årjäng",	"S+KD+L+M",	"22 av 35",
    "Bjurholm",	"M+C+L+KD",	"18 av 31",
    "Dorotea",	"DKL+L+C+KD",	"18 av 25",
    "Lycksele",	"S+V",	"16 av 31",
    "Malå",	"S+V",	"13 av 25",
    "Nordmaling",	"C+M+L+KD",	"18 av 31",
    "Norsjö",	"S",	"17 av 31",
    "Robertsfors",	"S",	"17 av 31",
    "Skellefteå",	"S",	"34 av 65",
    "Sorsele",	"V+C+M+KD",	"12 av 21",
    "Storuman",	"C+M+L+KD",	"20 av 41 (minoritet)",
    "Umeå",	"S+MP",	"28 av 65 (minoritet)",
    "Vilhelmina",	"S+V",	"13 av 27 (minoritet)",
    "Vindeln",	"S+V",	"16 av 31",
    "Vännäs",	"S+V+MP",	"18 av 35",
    "Åsele",	"ÅSP+C+L",	"15 av 31 (minoritet)",
    "Härnösand",	"S+MP+V",	"27 av 43",
    "Kramfors",	"S",	"20 av 41 (minoritet)",
    "Sollefteå",	"S+V",	"24 av 45",
    "Sundsvall",	"S+V+C",	"46 av 81",
    "Timrå",	"S+V",	"23 av 41",
    "Ånge",	"S",	"18 av 35",
    "Örnsköldsvik",	"S+V",	"31 av 61",
    "Arboga",	"S+V+C+OPA(2014–2016)",	"21 av 41",
    "Arboga",	"M+L+V+MP+C+KD+OPA(2016–)",	"21 av 41",
    "Fagersta",	"S+V(2014–2015)",	"24 av 35",
    "Fagersta",	"S+M(2015–)",	"18 av 35",
    "Hallstahammar",	"S+V+MP",	"27 av 45",
    "Kungsör",	"S+L+V+MP",	"21 av 39",
    "Köping",	"S+V+MP",	"26 av 49",
    "Norberg",	"S",	"12 av 31 (minoritet)",
    "Sala",	"C+M+SBÄ+L+KD",	"21 av 45 (minoritet)",
    "Skinnskatteberg",	"L+C+M",	"14 av 31 (minoritet)",
    "Surahammar",	"S+C",	"20 av 39",
    "Västerås",	"S+MP+C+KD",	"31 av 61",
    "Ale",	"S+V+MP",	"23 av 49 (minoritet)",
    "Alingsås",	"S+MP+V(2014–2016)",	"25 av 51 (minoritet)",
    "Alingsås",	"M+L+KD+C(2016–)",	"22 av 51 (minoritet)",
    "Bengtsfors",	"S+L+MP",	"16 av 31",
    "Bollebygd",	"S+MP+V",	"13 av 31 (minoritet)",
    "Borås",	"S+V+MP",	"35 av 73 (minoritet)",
    "Dals-Ed",	"C+M+KD+L",	"18 av 31",
    "Essunga",	"M+C+L+KD",	"18 av 31",
    "Falköping",	"S+C+KD",	"27 av 51",
    "Färgelanda",	"S+L+V",	"14 av 29 (minoritet)",
    "Grästorp",	"M+C",	"14 av 27",
    "Gullspång",	"S+C",	"17 av 31",
    "Göteborg",	"S+MP+V+FI",	"40 av 81 (minoritet)",
    "Götene",	"S+GÖF",	"19 av 41 (minoritet)",
    "Herrljunga",	"S+L+KVäl+MP",	"16 av 31",
    "Hjo",	"M+C+L+KD",	"17 av 31",
    "Härryda",	"M+C+L+SPP+KD",	"27 av 51",
    "Karlsborg",	"S+M",	"16 av 31",
    "Kungälv",	"S+L+UtvP+V+MP",	"36 av 59",
    "Lerum",	"S+MP+L+C",	"28 av 51",
    "Lidköping",	"S+V+MP",	"27 av 51",
    "Lilla Edet",	"S+V+L",	"15 av 31 (29+2 vakanta)",
    "Lysekil",	"S+L+M+C",	"14 av 31 (minoritet)",
    "Mariestad",	"M+L+C+KD",	"22 av 49 (minoritet)",
    "Mark",	"M+C+mbp+L+MP+KD",	"24 av 51 (minoritet)",
    "Mellerud",	"S+C",	"17 av 31",
    "Munkedal",	"S+C+MP",	"18 av 35",
    "Mölndal",	"S+MP+V+KD",	"32 av 61",
    "Orust",	"S+C+MP+FPO+V+OP",	"24 av 41",
    "Partille",	"M+L+KD+C",	"24 av 51 (minoritet)",
    "Skara",	"S+L+V+MP",	"22 av 45 (minoritet)",
    "Skövde",	"M+C+L+KD",	"29 av 61 (minoritet)",
    "Sotenäs",	"M+L+C+KD",	"17 av 31",
    "Stenungsund",	"M+L+C+KD(2014–2017)",	"19 av 41 (minoritet)",
    "Stenungsund",	"S+vildar+MP+V(2017–)",	"23 av 41",
    "Strömstad",	"C+L+MP+KD",	"20 av 39",
    "Svenljunga",	"S+LBPO+L",	"17 av 33",
    "Tanum",	"C+M+L+KD",	"24 av 41",
    "Tibro",	"S+C+MP+V",	"19 av 35",
    "Tidaholm",	"S+V",	"21 av 41",
    "Tjörn",	"M+L+C+KD+MP",	"22 av 41",
    "Tranemo",	"C+M+KD+L(2014–2016)",	"17 av 37 (minoritet",
    "Tranemo",	"S+MP+V+KD+L(2016–)",	"19 av 37",
    "Trollhättan",	"S+V+MP",	"35 av 61",
    "Töreboda",	"C+M",	"13 av 31 (minoritet)",
    "Uddevalla",	"S+V+MP",	"31 av 61",
    "Ulricehamn",	"S+V(2014–2016)",	"15 av 49 (minoritet)",
    "Ulricehamn",	"S+C+L(2016–)",	"25 av 49",
    "Vara",	"S+C+KD+V+MP",	"25 av 45",
    "Vårgårda",	"C+M+KD+L",	"21 av 41",
    "Vänersborg",	"S+C+MP",	"22 av 51 (minoritet)",
    "Åmål",	"S+MP+V",	"19 av 35",
    "Öckerö",	"M+KD+L",	"24 av 41",
    "Askersund",	"S+V+MP",	"17 av 33",
    "Degerfors",	"MP+V",	"14 av 31 (minoritet)",
    "Hallsberg",	"MP+S",	"22 av 45 (minoritet)",
    "Hällefors",	"M+S+Gl",	"17 av 31",
    "Karlskoga",	"V+S+L",	"25 av 47",
    "Kumla",	"M+S",	"26 av 45",
    "Laxå",	"M+KD+C+MP+L",	"16 av 31",
    "Lekeberg",	"M+C+KD+MP+L",	"18 av 35",
    "Lindesberg",	"C+S",	"24 av 45",
    "Ljusnarsberg",	"V+S+MP",	"13 av 25",
    "Nora",	"V+S",	"18 av 35",
    "Örebro",	"KD+S+C",	"32 av 65 (minoritet)",
    "Boxholm",	"S",	"19 av 35",
    "Finspång",	"S+V+MP",	"26 av 45",
    "Kinda",	"S+M+KD",	"19 av 35",
    "Linköping",	"S+MP+L",	"40 av 79",
    "Mjölby",	"S+C+KD+MP",	"24 av 45",
    "Motala",	"S+V+MP",	"30 av 57",
    "Norrköping",	"S+L+C+KD",	"43 av 85",
    "Söderköping",	"S+M+MP",	"25 av 39",
    "Vadstena",	"S+Kons",	"19 av 35",
    "Valdemarsvik",	"S+NB+MP+V",	"18 av 35",
    "Ydre",	"S+C+M+MP+KD+SD",	"21 av 21 (samstyre)",
    "Åtvidaberg",	"S+M",	"22 av 35",
    "Ödeshög",	"KD+M+C(2014–2016)",	"18 av 35",
    "Ödeshög",	"KD+S+C(2016–)",	"22 av 35"
)
```


## Scraping majorities 2010
From https://sv.wikipedia.org/wiki/Lista_%C3%B6ver_kommun-_och_landstingsstyren_i_Sverige_2010%E2%80%932014, copied into excel and cleaned by hand. This is due to the irregular table used by wikipedia, which makes web scraping beyond my capabilities. Risk of errors increase
```{r}
major_2010 <- tribble(
    ~municipality,  ~rule,                   ~num_mandates,
"Karlshamn",	"S+C+FP+KD",	"27 av 51",
"Karlskrona",	"M+FP+C+MP+KD",	"36 av 75 (minoritet)",
"Olofström",	"S",	"25 av 49",
"Ronneby",	"M+C+ROP+FP+KD",	"24 av 49 (minoritet)",
"Sölvesborg",	"S+V+MP",	"25 av 49",
"Avesta",	"S+V+MP",	"22 av 41",
"Borlänge",	"S+MP",	"26 av 61 (minoritet)",
"Falun",	"S+MP+V",	"31 av 61",
"Gagnef",	"C+M+KD+FP",	"20 av 35",
"Hedemora",	"S+LHP+MP+V",	"21 av 41",
"Leksand",	"C+M+KD+FP",	"30 av 49",
"Ludvika",	"S+V",	"26 av 45",
"Malung-Sälen",	"S+V+C",	"23 av 39",
"Mora",	"S+C",	"23 av 41",
"Orsa",	"S+M+MP+FP",	"16 av 31",
"Rättvik",	"C+M+FP+KD+SPI",	"20 av 39",
"Smedjebacken",	"S+V",	"23 av 35",
"Säter",	"S+FP+V+MP",	"20 av 35",
"Vansbro",	"C+KD+M+FP",	"15 av 31 (minoritet)",
"Älvdalen",	"C+M+KL+KD",	"18 av 35",
"Gotland",	"S+V+MP",	"37 av 71",
"Bollnäs",	"S+FP+V+SJVB+MP",	"24 av 45",
"Gävle",	"S+MP+V",	"33 av 65",
"Hofors",	"S+V+MP",	"18 av 31",
"Hudiksvall",	"C+M+MP+KD+FP",	"26 av 51",
"Ljusdal",	"S+SOCD+V(2010-2012)[2]",	"21 av 41",
"Ljusdal",	"S+V(2012-2014)[3]",	"17 av 41 (minoritet)",
"Nordanstig",	"S+C+M+V+MP",	"24 av 31",
"Ockelbo",	"S+C",	"20 av 31",
"Ovanåker",	"S+M+MP+FP",	"24 av 41",
"Sandviken",	"S+MP",	"24 av 51 (minoritet)",
"Söderhamn",	"S+V+MP",	"25 av 49",
"Falkenberg",	"C+M+FP+KD",	"27 av 51",
"Halmstad",	"M+FP+C+MP+KD",	"37 av 71",
"Hylte",	"C+KV+M+FP+KD",	"24 av 43[4]",
"Kungsbacka",	"M+FP+C+KD",	"39 av 61",
"Laholm",	"M+C+FP+KD",	"23 av 41",
"Varberg",	"M+C+FP+KD",	"31 av 61",
"Berg",	"S+C+FP",	"19 av 31",
"Bräcke",	"S",	"22 av 41",
"Härjedalen",	"S+C+V+FP",	"25 av 39",
"Krokom",	"C+M+MP+FP+KD",	"24 av 45",
"Ragunda",	"S",	"18 av 31",
"Strömsund",	"S+V",	"20 av 35",
"Åre",	"C+M+VV+FP+KD",	"23 av 41",
"Aneby",	"C+KD+M+FP",	"21 av 35",
"Eksjö",	"S+C+M",	"36 av 49",
"Gislaved",	"M+C+KD+FP+MP",	"26 av 49",
"Gnosjö",	"M+KD+C+FP",	"21 av 35",
"Habo",	"M+KD+FP+C",	"22 av 35",
"Jönköping",	"M+KD+FP+C+MP",	"48 av 81",
"Mullsjö",	"M+KD+FP+C+MP",	"17 av 35 (minoritet)",
"Nässjö",	"S+C+FP+V",	"30 av 57",
"Sävsjö",	"KD+M+C+FP",	"27 av 45",
"Tranås",	"M+KD+C+FP+MP",	"20 av 41 (minoritet)",
"Vaggeryd",	"S+C+V+MP",	"22 av 41",
"Vetlanda",	"S+M+C",	"26 av 45",
"Värnamo",	"C+M+KD+FP",	"29 av 51",
"Borgholm",	"C+M+KD+FP",	"23 av 41",
"Emmaboda",	"S+MP",	"21 av 41",
"Hultsfred",	"C+M+KD+MP+FP",	"25 av 45",
"Högsby",	"S+MP+V",	"19 av 41 (minoritet)",
"Kalmar",	"S+MP+V(2010-2012)",	"35 av 61",
"Kalmar",	"S+V(2012-2013)",	"31 av 61",
"Kalmar",	"S+C+V(2013-2014)",	"36 av 61",
"Mönsterås",	"C+M+KD+FP",	"26 av 49",
"Mörbylånga",	"M+C+KD",	"24 av 49",
"Nybro",	"S+V+MP(2010–2011)",	"25 av 49",
"Nybro",	"S(2011-2012)",	"21 av 49 (minoritet)",
"Nybro",	"S+M(2012-2014)",	"30 av 49",
"Oskarshamn",	"S+V+MP",	"27 av 49",
"Torsås",	"C+M+KD+FP",	"18 av 35",
"Vimmerby",	"M+C+KD+FP",	"26 av 49",
"Västervik",	"M+C+FP+VDM+KD",	"29 av 57",
"Alvesta",	"M+FP+KD",	"15 av 49 (minoritet)",
"Lessebo",	"S",	"16 av 35 (minoritet)",
"Ljungby",	"M+C+FP+KD+MP",	"25 av 49",
"Markaryd",	"KD+M+C",	"21 av 35",
"Tingsryd",	"M+S+KD+FP",	"25 av 41",
"Uppvidinge",	"C+M+KD+MP+FP",	"18 av 35",
"Växjö",	"M+C+FP+KD",	"31 av 61",
"Älmhult",	"M+C+KD+MP+FP",	"23 av 41",
"Arjeplog",	"S",	"17 av 31",
"Arvidsjaur",	"S+V",	"19 av 31",
"Boden",	"S+V",	"26 av 49",
"Gällivare",	"S",	"21 av 41",
"Haparanda",	"S",	"21 av 35",
"Jokkmokk",	"S+FJK",	"18 av 31",
"Kalix",	"S+MP+V",	"24 av 45",
"Kiruna",	"S+V+SL",	"24 av 45",
"Luleå",	"S+MP",	"36 av 61",
"Pajala",	"S+V",	"25 av 33",
"Piteå",	"S",	"30 av 51",
"Älvsbyn",	"S",	"13 av 31 (minoritet)",
"Överkalix",	"S",	"18 av 31",
"Övertorneå",	"S+V+ÖFA",	"21 av 31",
"Bjuv",	"S+V",	"14 av 31 (minoritet)",
"Bromölla",	"S",	"16 av 41 (minoritet)",
"Burlöv",	"S",	"14 av 41 (minoritet)",
"Båstad",	"M+C+FP+KD",	"23 av 41",
"Eslöv",	"S+M",	"27 av 49",
"Helsingborg",	"M+FP+KD",	"30 av 65 (minoritet)",
"Hässleholm",	"M+C+KD+FP+FOV",	"28 av 61 (minoritet)",
"Höganäs",	"M+FP+C+KD",	"27 av 41",
"Hörby",	"M+C+MP+FP+KD",	"24 av 41",
"Höör",	"M+FP+C+KD",	"21 av 41",
"Klippan",	"M+C+KD+FP+MP",	"21 av 41",
"Kristianstad",	"M+FP+C+MP+ÅHP",	"36 av 71",
"Kävlinge",	"M+FP+C+KD",	"25 av 49",
"Landskrona",	"FP+M+MP",	"22 av 51 (minoritet)",
"Lomma",	"M",	"24 av 45",
"Lund",	"M+FP+C+KD",	"33 av 65",
"Malmö",	"S+MP+V",	"31 av 61",
"Osby",	"C+KD+M+FP+MP+GKS",	"20 av 41 (minoritet)",
"Perstorp",	"pf+M+C+FP+KD",	"19 av 35",
"Simrishamn",	"M+C+ÖSTP+FP+KD",	"25 av 49",
"Sjöbo",	"M+C+FP",	"21 av 49",
"Skurup",	"M+FP+C+MP",	"21 av 41",
"Staffanstorp",	"M+Staffanstorpspartiet",	"20 av 41 (minoritet)",
"Svalöv",	"S+M+FP",	"20 av 35",
"Svedala",	"M+C+FP+BAP",	"23 av 45",
"Tomelilla",	"S+M",	"22 av 41",
"Trelleborg",	"M+FP+MP+KD+C",	"24 av 51 (minoritet)",
"Vellinge",	"M",	"28 av 51",
"Ystad",	"M+C+FP+KD+MP",	"26 av 49",
"Åstorp",	"S+C",	"16 av 31",
"Ängelholm",	"M+C+FP+KD",	"28 av 51",
"Örkelljunga",	"M+FP+KD+C+SPI",	"25 av 45",
"Östra Göinge",	"M+FP+C+KD+MP",	"16 av 31",
"Botkyrka",	"S+MP+V",	"32 av 61",
"Danderyd",	"M+KD+C",	"32 av 45[10]",
"Ekerö",	"M+C+FP+KD",	"26 av 41",
"Haninge",	"M+FP+MP+KD+C",	"33 av 61",
"Huddinge",	"M+FP+DP+KD+C",	"33 av 61",
"Järfälla",	"M+FP+KD+C",	"32 av 61",
"Lidingö",	"M+FP+KD",	"27 av 51",
"Nacka",	"M+FP+C+KD",	"40 av 61",
"Norrtälje",	"M+C+FP+KD",	"34 av 61",
"Nykvarn",	"NP+M+FP+C",	"18 av 31",
"Nynäshamn",	"S+FP",	"18 av 41 (minoritet)",
"Salem",	"M+FP+C+KD",	"18 av 31",
"Sigtuna",	"S+MP+C",	"26 av 51",
"Sollentuna",	"M+FP+KD",	"35 av 61",
"Solna",	"M+FP+KD+C",	"36 av 61",
"Stockholm",	"M+FP+C+KD",	"52 av 101",
"Sundbyberg",	"S+MP+KD+C",	"25 av 51 (minoritet)",
"Södertälje",	"S+MP+V",	"34 av 65",
"Tyresö",	"M+FP+KD+C",	"29 av 51",
"Täby",	"M+FP+C+KD",	"49 av 61",
"Upplands-Bro",	"M+FP+KD+C",	"21 av 41",
"Upplands-Väsby",	"M+FP+KD+C",	"27 av 51",
"Vallentuna",	"M+C+FP+KD",	"26 av 51",
"Vaxholm",	"M+C+FP",	"21 av 31",
"Värmdö",	"M+MP+FP+KD",	"30 av 51",
"Österåker",	"M+FP+C+KD+ÖP",	"31 av 51",
"Eskilstuna",	"S+MP+V",	"41 av 79",
"Flen",	"S+A2000+V",	"24 av 45",
"Gnesta",	"S+MP+V",	"16 av 31",
"Katrineholm",	"S+M",	"31 av 51",
"Nyköping",	"S+MP+V",	"32 av 61",
"Oxelösund",	"S+V",	"16 av 31",
"Strängnäs",	"S+C+FP+MP",	"29 av 55",
"Trosa",	"M+FP+C+KD",	"22 av 35",
"Vingåker",	"S",	"15 av 35 (minoritet)",
"Enköping",	"M+C+KD",	"25 av 51 (minoritet)",
"Heby",	"C+M+FP+KD+MP",	"20 av 41 (minoritet)",
"Håbo",	"S+BÅP+MP+V",	"21 av 41",
"Knivsta",	"M+KNU+FP+C+KD",	"21 av 31",
"Tierp",	"S+MP+V",	"27 av 49",
"Uppsala",	"M+FP+C+KD",	"41 av 81",
"Älvkarleby",	"S+V",	"16 av 31",
"Östhammar",	"S+C",	"28 av 49",
"Arvika",	"S",	"23 av 49",
"Eda",	"C+M+KD+FP",	"16 av 35 (minoritet)",
"Filipstad",	"S+V+MP",	"22 av 37",
"Forshaga",	"S",	"22 av 41",
"Grums",	"S",	"17 av 31",
"Hagfors",	"S+V",	"22 av 35",
"Hammarö",	"M+KD+FP+MP+C",	"17 av 31",
"Karlstad",	"M+MP+FP+C+KD",	"32 av 61",
"Kil",	"S+C",	"19 av 35",
"Kristinehamn",	"S+V+MP",	"21 av 41",
"Munkfors",	"S",	"17 av 31",
"Storfors",	"S",	"16 av 31",
"Sunne",	"C+M+FP",	"23 av 41",
"Säffle",	"C+M+MP+FP+KD",	"21 av 41",
"Torsby",	"S",	"15 av 31 (minoritet)",
"Årjäng",	"C+FP+M+KD",	"22 av 41",
"Bjurholm",	"M+C+FP+KD",	"20 av 31",
"Dorotea",	"S+V",	"17 av 31",
"Lycksele",	"S+V+MP",	"24 av 41",
"Malå",	"S+V",	"18 av 31",
"Nordmaling",	"S+V",	"16 av 31",
"Norsjö",	"S",	"17 av 31",
"Robertsfors",	"S+V",	"16 av 31",
"Skellefteå",	"S",	"33 av 65",
"Sorsele",	"S+V",	"19 av 31",
"Storuman",	"C+M+FP+KD+SKL",	"22 av 41",
"Umeå",	"S+V",	"32 av 65 (minoritet)",
"Vilhelmina",	"S+V",	"21 av 35",
"Vindeln",	"C+M+KD+FP",	"17 av 31",
"Vännäs",	"Oklart",	
"Åsele",	"S",	"16 av 31",
"Härnösand",	"S+V+MP",	"24 av 43",
"Kramfors",	"S+V",	"24 av 41",
"Sollefteå",	"S+V",	"24 av 45",
"Sundsvall",	"M+FP+MP+C+KD",	"41 av 81",
"Timrå",	"S",	"24 av 49 (minoritet)",
"Ånge",	"S",	"20 av 35",
"Örnsköldsvik",	"S",	"31 av 61",
"Arboga",	"S+V+C+OPA",	"22 av 41",
"Fagersta",	"V",	"20 av 35",
"Hallstahammar",	"S+V",	"26 av 45",
"Kungsör",	"S",	"13 av 39 (minoritet)",
"Köping",	"S+V+MP",	"28 av 49",
"Norberg",	"S+MP",	"15 av 31 (minoritet)",
"Sala",	"S+SBÄ+V+MP",	"24 av 45",
"Skinnskatteberg",	"S+V+MP",	"16 av 31",
"Surahammar",	"S+V+MP",	"24 av 39",
"Västerås",	"S+MP+V",	"30 av 61 (minoritet)",
"Ale",	"M+ADK+FP+C+KD",	"24 av 49 (minoritet)",
"Alingsås",	"M+FP+KD+C",	"26 av 51",
"Bengtsfors",	"S+FP+MP",	"18 av 35",
"Bollebygd",	"M+C+KD+FP",	"16 av 31",
"Borås",	"S+V+MP+VÄG",	"35 av 73 (minoritet)",
"Dals-Ed",	"C+M+KD+FP",	"19 av 31",
"Essunga",	"M+KD+FP",	"13 av 31",
"Falköping",	"S+C+KD",	"27 av 51",
"Färgelanda",	"C+M+KD",	"18 av 35",
"Grästorp",	"M+C+FP",	"20 av 31",
"Gullspång",	"S+C+MP",	"21 av 31",
"Göteborg",	"S+MP+V",	"41 av 81",
"Götene",	"S+GÖF+V",	"21 av 41",
"Herrljunga",	"C+M+FP+KD",	"19 av 41 (minoritet)",
"Hjo",	"M+FP+C+KD",	"18 av 33",
"Härryda",	"M+FP+C+KD",	"27 av 51",
"Karlsborg",	"C+M+FP+KD",	"17 av 31",
"Kungälv",	"M+FP+C+KD",	"28 av 59 (minoritet)",
"Lerum",	"M+FP+C+KD",	"29 av 51",
"Lidköping",	"S+V+MP",	"28 av 51",
"Lilla Edet",	"S+V+FP",	"17 av 31",
"Lysekil",	"Oklart (2010-2013)",	
"Lysekil",	"S+M+MP+V+SKÖP (2013-2014)[11]",	"23 av 31",
"Mariestad",	"S+V+MAP+MP",	"27 av 49",
"Mark",	"M+C+FP+KD+MP",	"24 av 51 (minoritet)",
"Mellerud",	"C+M+KD+FP",	"20 av 41 (minoritet)",
"Munkedal",	"S+C",	"18 av 35",
"Mölndal",	"M+FP+KD+C",	"32 av 61",
"Orust",	"S+FPO+FP (2010-2011)[12]",	"21 av 41",
"Orust",	"M+FPO+C+MP+KD+V+OP (2012-2014)[12]",	"24 av 41",
"Partille",	"M+FP+KD+C",	"27 av 51",
"Skara",	"M+C+FP+KD (2010-2013)[13]",	"22 av 45 (minoritet)",
"Skara",	"S+MP+FP+V (2014)[13]",	"23 av 45",
"Skövde",	"M+C+FP+KD",	"32 av 61",
"Sotenäs",	"M+FP+KD+C+NSP",	"19 av 31",
"Stenungsund",	"M+FP+C+KD",	"22 av 41",
"Strömstad",	"S+M+STRÖP",	"22 av 39",
"Svenljunga",	"C+M+FP+KD",	"19 av 33",
"Tanum",	"C+M+FP+KD",	"27 av 41",
"Tibro",	"FP+M+KD+C",	"20 av 35",
"Tidaholm",	"S",	"20 av 41 (minoritet)",
"Tjörn",	"M+FP+KD+SB+C",	"22 av 41",
"Tranemo",	"C+M+FP+KD",	"19 av 37",
"Trollhättan",	"S",	"31 av 61",
"Töreboda",	"S+V+FP+MP",	"16 av 31",
"Uddevalla",	"S+V+FP+MP",	"31 av 61",
"Ulricehamn",	"M+FP+KD",	"18 av 49 (minoritet)",
"Vara",	"S+C+V+KD+MP",	"25 av 45",
"Vårgårda",	"M+C+KD+FP",	"23 av 41",
"Vänersborg",	"Oklart",	
"Åmål",	"S+MP+V",	"18 av 35",
"Öckerö",	"M+KD+FP",	"27 av 41",
"Askersund",	"S+V+MP",	"17 av 33",
"Degerfors",	"V+MP",	"21 av 41",
"Hallsberg",	"S",	"23 av 45",
"Hällefors",	"S+HOB+V+C",	"22 av 31",
"Karlskoga",	"S+V",	"27 av 51",
"Kumla",	"S",	"22 av 45 (minoritet)",
"Laxå",	"S+V",	"17 av 31",
"Lekeberg",	"C+M+KD+FP",	"17 av 35 (minoritet)",
"Lindesberg",	"S+MP+V",	"23 av 45",
"Ljusnarsberg",	"S+MP+V",	"18 av 31",
"Nora",	"M+NOR+C+FP+KD+MP",	"18 av 35",
"Örebro",	"S+C+KD",	"34 av 65",
"Boxholm",	"S",	"19 av 35",
"Finspång",	"S+V+MP",	"26 av 45",
"Kinda",	"C+M+MP+KD",	"21 av 35",
"Linköping",	"M+FP+C+KD",	"41 av 79",
"Mjölby",	"S+V+MP",	"22 av 45 (minoritet)",
"Motala",	"S+V+MP",	"32 av 57",
"Norrköping",	"S+MP+V",	"43 av 85",
"Söderköping",	"M+C+FP+KD",	"22 av 39",
"Vadstena",	"M+KD+FP+C",	"18 av 35",
"Valdemarsvik",	"NB+C+M+KD+FP",	"19 av 35",
"Ydre",	"C+M+KD",	"17 av 31",
"Åtvidaberg",	"S+M",	"25 av 35",
"Ödeshög",	"KD+M+C+FP",	"20 av 35"
)
```

## Scraping majorities 2006
From https://sv.wikipedia.org/wiki/Lista_%C3%B6ver_kommun-_och_landstingsstyren_i_Sverige_2006%E2%80%932010, copied into excel and cleaned by hand. This is due to the irregular table used by wikipedia, which makes web scraping beyond my capabilities. Risk of errors increase
```{r}
major_2006 <- tribble(
    ~municipality,
    "Karlshamn: (s)+(fp)+(kd)",
"Karlskrona: (m)+(fp)+(c)+(kd)+(mp)",
"Olofström: (s)",
"Ronneby:(s)+(fp)+(kd)",
"Sölvesborg: (s)+(v)+(söp)",
"Avesta: (s)+(v)+(mp)",
"Borlänge: (s)+(mp) (minoritet)",
"Falun: (m)+(fp)+(c)+(kd)+(Falupartiet)",
"Gagnef: (c)+(m)+(fp)+(kd)",
"Hedemora: (s)+(v)+(mp)",
"Leksand: (c)+(m)+(fp)+(kd)",
"Ludvika: (s)+(v)",
"Malung: (s)+(c)+(v) (2006-sommaren 2008),(m)+(fp)+(c)+(kd)+(m s p)[1]",
"Mora: (c)+(s)",
"Orsa: (s)+(v)+(mp)",
"Rättvik: (c)+(m)+(fp)+(kd)+(mp)+(spi)",
"Smedjebacken: (s)+(v)",
"Säter: (s)+(fp)+(v)+(mp)",
"Vansbro: (kd+(c))+(m)+(fp)",
"Älvdalen: (s)+(fp)+(mp)",
"Gotland: (c)+(m)+(fp)+(kd)",
"Bollnäs: (c)+(s)",
"Gävle: (s)+(v)+(mp)",
"Hofors: (s)+(v)+(mp)",
"Hudiksvall: (s)+(v)",
"Ljusdal: (s)+(fp)+(c)",
"Nordanstig: (c)+(m)+(kd)",
"Ockelbo: (s)",
"Ovanåker: (m)+(fp)+(c)+(kd)",
"Sandviken: (s)+(c)",
"Söderhamn: (s)+(c)",
"Falkenberg: (m)+(fp)+(c)+(kd)+(Aktiv Politik)",
"Halmstad: (m)+(fp)+(c)+(kd)+(Spi)",
"Hylte: (c)+ (S)+ (Medansvar( )",
"Kungsbacka: (m)+(fp)+(c)+(kd)",
"Laholm: (m)+(fp)+(c)+(kd)",
"Varberg: (m)+(fp)+(c)+(kd)+(Spi)",
"Berg: (be)+(c)+(m)+(kd)",
"Bräcke: (s)+(v)",
"Härjedalen: (s)+(c)+(v)+(fp)",
"Krokom: (c)+(m)+(fp)+(kd)+(mp)",
"Ragunda: (s)+(c)",
"Strömsund: (c)+(m)+(fp) (minoritet)",
"Åre: (c)+(m)+(fp)+(kd)",
"Östersund: (s)+(v)+(mp)",
"Aneby: (c)+(m)+(kd)+(fp)",
"Eksjö: (c)+(m)+(kd)+(fp)",
"Gislaved: (m)+(kd)+(c)+(fp)",
"Gnosjö: (kd)+(m)+(c)+(fp)",
"Habo: (m)+(kd)+(c)+(fp)",
"Jönköping: (m)+(kd)+(c)+(fp)+(mp)",
"Mullsjö: (m)+(c)+(fp)+(mf)",
"Nässjö: (s)+(v)+(safe)",
"Sävsjö: (kd)+(m)+(c)+(fp)",
"Tranås: (m)+(kd)+(c)+(fp)",
"Vaggeryd: (m)+(kd)+(c)+(fp)",
"Vetlanda: (c)+(m)+(kd)+(fp)",
"Värnamo: (c)+(m)+(kd)+(fp)",
"Borgholm: (c)+(m)+(kd)+(fp)+(mp)",
"Emmaboda: (s)+(v)",
"Hultsfred: (s)+(v)",
"Högsby: (c)+(m)+(kd)+(fp)+(mp)+(lhk)",
"Kalmar: (s)+(v)+(mp)",
"Mönsterås: (c)+(m)+(kd)+(fp)",
"Mörbylånga: (m)+(c)+(kd)+(fp)+(mp)+(ölp)",
"Nybro: (s)+(v)+(mp)",
"Oskarshamn: (s)+(v)",
"Torsås: (s) (minoritet)",
"Vimmerby: (c)+(m)+(kd)+(fp)",
"Västervik: (m)+(c)+(kd)+(fp)+(vdm)",
"Alvesta: (s)+(c)+(fp)+(mp)",
"Lessebo: (s)",
"Ljungby: (c)+(m)+(kd)+(fp) (minoritet)",
"Markaryd: (kd)+(m)+(c)+(fp)",
"Tingsryd: (m)+(c)+(kd)+(fp)",
"Uppvidinge: (c)+(m)+(kd)+(fp)",
"Växjö: (m)+(c)+(kd)+(fp) (minoritet)",
"Älmhult: (c)+(m)+(kd)+(fp)+(mp)",
"Arjeplog: (s)+(v)",
"Arvidsjaur: (s)",
"Boden: (m)+(v)+(ns)+(c)+(mp)+(fp) (2006-mars 2009), (m)+(ns)+(c)+(kd)+(fp) (mars 2009-)",
"Gällivare: (s)+(v)",
"Haparanda: (s)",
"Jokkmokk: (v)+(fp)+(sv)+(mp)+(alt)+(c)+(m)",
"Kalix: (s)",
"Kiruna: (s)+(kip)",
"Luleå: (s)",
"Pajala: (s)+(v)",
"Piteå: (s)",
"Älvsbyn: (s)",
"Överkalix: (s)",
"Övertorneå: (c)+(kd)+(m)+(öa)+(ns)",
"Bjuv: (s)+(v)",
"Bromölla: (s)",
"Burlöv: (s)+(m)+(kd)",
"Båstad: (m)+(fp)+(bp)",
"Eslöv: (s)+(v)+(mp) (minoritet)",
"Helsingborg: (m)+(c)+(kd)+(fp)+(spi)",
"Hässleholm: (m)+(c)+(kd)+(fp)+(fv",
"Höganäs: (m)+(fp)+(c)+(kd)",
"Hörby: (m)+(c)+(fp)+(kd)+(mp)",
"Höör: (m)+(fp)+(c)+(kd)+(spi)",
"Klippan: (m)+(fp)+(c)+(kd)",
"Kristianstad: (m)+(c)+(fp)+(åå)+(kbf)",
"Kävlinge: (m)+(c)+(fp)+(kd) (minoritet)",
"Landskrona: (fp)+(m)+(mp) (minoritet)",
"Lomma: (m)+(fp)",
"Lund: (m)+(c)+(fp)+(kd)",
"Malmö: (s)+(v)+(mp)",
"Osby: (m)+(fp)+(c)+(kd) (minoritet)",
"Perstorp: (s)+(v) (minoritet)",
"Simrishamn: (m)+(fp)+(c)+(kd)+(svp)[förtydliga]",
"Sjöbo: (m)+(c)+(fp) (minoritet)",
"Skurup: (m)+(fp)+(c)+(kd)+(kv)",
"Staffanstorp: (m)+(fp)+(kd) (minoritet)",
"Svalöv: (s)+(m) (sedan 2004)",
"Svedala: Hoppande majoritet",
"Tomelilla: (m)+(fp)+(c)+(kd)+(kv)",
"Trelleborg: (m)+(fp)+(c)+(kd)+(mp)+(spi) (minoritet)",
"Vellinge: (m)",
"Ystad: (m)+(c)+(fp)+(kd)+(spi)",
"Åstorp: (s)+(c)",
"Ängelholm: (m)+(kd)+(fp)+(c)+(spi)",
"Örkelljunga: (m)+(c)+(kd)+(spi)",
"Östra Göinge: (s) (minoritet)",
"Botkyrka: (s)+(v)+(mp)",
"Danderyd: (m)+(kd)",
"Ekerö: (m)+(fp)+(c)+(kd)",
"Haninge: (m)+(fp)+(c)+(kd)+(mp)",
"Huddinge: (m)+(fp)+(kd)+(dp)",
"Järfälla: (m)+(fp)+(c)+(kd)",
"Lidingö: (m)+(fp)",
"Nacka: (m)+(fp)+(kd)",
"Norrtälje: (m)+(fp)+(c)+(kd)",
"Nykvarn: (np)+(m)+(c)",
"Nynäshamn: (s)+(fp)",
"Salem: (m)+(fp)+(c)+(kd)",
"Sigtuna: (s)+(c)+(mp)",
"Sollentuna: (m)+(fp)+(c)+(kd)",
"Solna: (m)+(fp)+(kd)",
"Stockholm: (m)+(kd)+(fp)",
"Sundbyberg: (s)+(v)+(mp)+partilösa",
"Södertälje: (s)+(v)+(mp)",
"Tyresö: (m)+(fp)+(kd)+(c)",
"Täby: (m)+(fp)+(kd)+(c)",
"Upplands-Bro: (fp)+(s)",
"Upplands-Väsby: (m)+(fp)+(kd)+(c)",
"Vallentuna: (m)+(fp)+(kd)+(c)",
"Vaxholm: (m)+(fp)+(c)+(kd)",
"Värmdö: (m)+(fp)+(c)+(kd)",
"Österåker: (m)+(fp)+(c)+(kd)+(Österåkerspartiet)",
"Eskilstuna: (s)+(v)",
"Flen: (s)+(Alternativ 2000)",
"Gnesta: (m)+(kd)+(c)+(fp)",
"Katrineholm: (s)",
"Nyköping: (m)+(c)+(kd)+(fp)+(mp)",
"Oxelösund: (s) (minoritet)",
"Strängnäs: (c)+(fp)+(s)",
"Trosa: (m)+(kd)+(c)+(fp)",
"Vingåker: (s)",
"Enköping: (m)+(fp)+(c)+(kd)",
"Heby: (s)+(m)+(v)+(fp)",
"Håbo: (m)+(fp)+(kd)+(Bålstapartiet)",
"Knivsta: (m)+(fp)+(c)+(kd)",
"Tierp: (s)+(v) (minoritet)",
"Uppsala: (m)+(fp)+(c)+(kd)",
"Älvkarleby: (s)+(v)",
"Östhammar: (c)+(m)+(fp)+(kd)+(mp)+(Borgerligt alternativ)",
"Arvika: (s)+(v)+(mp)",
"Eda: (s)+(hel)",
"Filipstad: (s)",
"Forshaga: (s)",
"Grums: (s)",
"Hagfors: (s)",
"Hammarö: (s)+(v)+(mp)",
"Karlstad: (s)+(v)+(mp)",
"Kil: (s)+(c)+(kd)",
"Kristinehamn: (m)+(c)+(kd)+(fp)+(Sjukvårdspartiet i Värmland)",
"Munkfors: (s)+(v) [2]",
"Storfors: (s)+(v)",
"Sunne: (c)+(m)+(kd)+(fp)",
"Säffle: (c)+(m)+(kd)+(fp)",
"Torsby: (s) (minoritet)[3]",
"Årjäng: (c)+(m)+(kd)+(fp)",
"Bjurholm: (m)+(c)+(kd)+(fp)",
"Dorotea: (dkl)+(c)+(fp)",
"Lycksele: (s)",
"Malå: (Malålistan)+(c)+(kd)+(fp)",
"Nordmaling: (c)+(m)+(kd)+(fp)",
"Norsjö: (s)+(v)",
"Robertsfors: (c)+(m)+(kd)",
"Skellefteå: (s)",
"Sorsele: (c)+(m)+(kd)+(fp)",
"Storuman:(m)+(c)+(kd)+(fp)+(v) (2006-mars 2008), (s)+(kd)+(kl) (mars 2008-)[4]",
"Umeå: (s) (minoritet)",
"Vilhelmina: (c)+(m)+(kd)+(fp)",
"Vindeln: (c)+(s)",
"Vännäs: (s)+(v)+(mp)",
"Åsele: (s)+(v)",
"Härnösand: (m)+(c)+(fp)+(kd)+(svp)",
"Kramfors: (s)+(v)",
"Sollefteå: (s)+(v)",
"Sundsvall: (s)+(v)+(mp)",
"Timrå: (s)",
"Ånge: (s)",
"Örnsköldsvik: (s)",
"Arboga: (s)+(v)",
"Fagersta: (v)",
"Hallstahammar: (s)+(v)",
"Kungsör: (s)+(c)",
"Köping: (s)+(v)+(mp)",
"Norberg: (s)+(v)",
"Sala: (c)+(m)+(fp)+(kd)",
"Skinnskatteberg: (fp)+(m)+(c)+(kd)+(Skinnskattebergsdemokraterna), sedan 16 februari 2009 (s)+(v)+(Skinnskattebergsdemokraterna)",
"Surahammar: (s)",
"Västerås: (m)+(c)+(fp)+(kd)+(mp)",
"Ale: (s)+(v)+(mp)",
"Alingsås: (m)+(c)+(fp)+(kd)",
"Bengtsfors: (c)+(m)+(fp)+(kd)",
"Bollebygd: (m)+(c)+(fp)+(kd)",
"Borås: (m)+(c)+(fp)+(kd)+(mp)+(Vägvalet)",
"Dals-Ed: (c)+(m)+(kd)",
"Essunga: (c)+(m)+(kd)",
"Falköping: (c)+(m)+(fp)+(kd) (minoritet)",
"Färgelanda: (c)+(m)+(fp)+(kd)",
"Grästorp: (c)+(m)+(fp)+(kd)",
"Gullspång: (s)+(c) (minoritet)",
"Göteborg: (s)+(mp) Sedan maj 2007",
"Götene: (m)+(c)+(fp)+(kd)",
"Herrljunga: (c)+(m)+(fp)+(kd) (minoritet)",
"Hjo: (m)+(c)+(fp)+(kd)",
"Härryda: (m)+(c)+(fp)+(kd)",
"Karlsborg: (c)+(m)+(fp)+(kd)",
"Kungälv: (m)+(c)+(fp)+(kd)",
"Lerum: (m)+(c)+(fp)+(kd)",
"Lidköping: (s)+(v)+(mp)",
"Lilla Edet: (c)+(m)+(fp)+(kd)+(mp)",
"Lysekil: (fp)+(c)+(m)+(kd) (minoritet)",
"Mariestad: (s)+(c)+(mp) (minoritet)",
"Mark: (s)+(v) (minoritet)",
"Mellerud: (c)+(m)+(fp)+(kd)",
"Munkedal: (m)+(c)+(kd)+(mp)+(Kommunal Samverkan Folket i Fokus)",
"Mölndal: (m)+(c)+(fp)+(kd)+(Kommunpartiet i Mölndal)",
"Orust: (m)+(c)+(fp)+(kd)",
"Partille: (m)+(c)+(fp)+(kd)",
"Skara: (m)+(c)+(fp)+(kd)",
"Skövde: (m)+(c)+(fp)+(kd)",
"Sotenäs: (m)+(c)+(fp)+(kd)+(nsp)",
"Stenungsund: (m)+(c)+(fp)+(kd)+(mp)",
"Strömstad: (s)+(Strömstadspartiet)+(v)",
"Svenljunga: (c)+(m)+(fp)+(kd)",
"Tanum: (c)+(m)+(fp)+(kd)",
"Tibro: (fp)+(m)+(c)+(kd)",
"Tidaholm: (s)",
"Tjörn: (s)+(c)+(fp)+(mp)+(Samhällets Bästa)",
"Tranemo: (c)+(m)+(fp)+(kd)",
"Trollhättan: (s)",
"Töreboda: (s)+(c)",
"Uddevalla: m)+(c)+(fp)+(kd)+(Uddevallapartiet)",
"Ulricehamn: (c)+(m)+(fp)+(kd)",
"Vara: (m)+(c)+(fp)",
"Vårgårda: (c)+(m)+(fp)+(kd)",
"Vänersborg: (s)+(c)",
"Åmål: (c)+(fp)+(kd)",
"Öckerö: (m)+(fp)+(kd)",
"Askersund: (s)+(c)",
"Degerfors: (s)+(m)+(c)+(fp)+(kd)",
"Hallsberg: (s)",
"Hällefors: (s) (minoritet)",
"Karlskoga: (s)",
"Kumla: (s)",
"Laxå: (s)+(v)",
"Lekeberg: (c)+(m)+(fp)+(kd)",
"Lindesberg: (c)+(m)+(fp)+(kd)+(v)",
"Ljusnarsberg: (s)+(v)",
"Nora: (s)+(v)",
"Örebro: (fp)+(m)+(c)+(kd)+(mp)",
"Boxholm: (s)",
"Finspång: (s)+(v) (2006-2008), (m)+(kd)+(fp)+(c)+(v) (2008-)",
"Kinda: (c)+(m)+(kd)+(fp)",
"Linköping: (m)+(kd)+(fp)+(c)",
"Mjölby: (m)+(kd)+(fp)+(c)+(spi)",
"Motala: (m)+(fp)+(c)+(kd)+(mp)+(spi)",
"Norrköping: (s)+(v)+(mp) (minoritet)",
"Söderköping: (c)+(m)+(kd)+(fp)",
"Vadstena: (m)+(s)",
"Valdemarsvik: (c)+(m)+(kd)+(fp)",
"Ydre: (c)+(s)+(m)+(kd)+(Folk och Miljö)",
"Åtvidaberg: (s)+(m)",
"Ödeshög: (kd)+(c)+(m)+(fp)"
) %>% separate(municipality, c("municipality", "majority"), sep = ":")
```




